\documentclass[11pt,fleqn]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{listings}
\usepackage{color}

\lstset{language=python,basicstyle=\ttfamily,breaklines=true,showspaces=false,showstringspaces=false,breakatwhitespace=true,texcl=true,escapeinside={\%*}{*)}}

\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}

\renewcommand{\labelenumi}{\theenumi.}
\renewcommand{\labelenumii}{\theenumii.}
\renewcommand{\labelenumiii}{\theenumiii.}
\newcommand{\be}{\begin{enumerate}}
	\newcommand{\ee}{\end{enumerate}}
\newcommand{\bi}{\begin{itemize}}
	\newcommand{\ei}{\end{itemize}}
\newcommand{\bc}{\begin{center}}
	\newcommand{\ec}{\end{center}}
\newcommand{\bsp}{\begin{sloppypar}}
	\newcommand{\esp}{\end{sloppypar}}
\newcommand{\sglsp}{\ }
\newcommand{\dblsp}{\ \ }
\newcommand{\mdot}{\mathrel.}
\newcommand{\mname}[1]{\mbox{\sf #1}}
\newcommand{\ForallApp}{\forall\,}
\newcommand{\ImpliesAlt}{\Rightarrow}
\newenvironment{proof}{\par\noindent{\bf Proof\sglsp}}{\hfill$\Box$}
\newcommand{\pnote}[1]{{\langle \text{#1} \rangle}} 

\begin{document}
	
	\begin{center}
		
		{\large \textbf{COMPSCI/SFWRENG 2FA3}}\\[2mm]
		{\large \textbf{Discrete Mathematics with Applications II}}\\[2mm]
		{\large \textbf{Winter 2021}}\\[8mm]
		{\huge \textbf{Assignment 6}}\\[6mm]
		{\large \textbf{Dr.~William M. Farmer and Dr.~Mehrnoosh Askarpour}}\\[2mm]
		{\large \textbf{McMaster University}}\\[6mm]
		{\large Revised: March 10, 2021}
		
	\end{center}
	
	\medskip
	
	Assignment 6 consists of two problems.  You must write your solutions
	to the problems using LaTeX.
	
	Please submit Assignment~6 as two files,
	\texttt{Assignment\_6\_\emph{YourMacID}.tex} and
	\texttt{Assignment\_6\_\emph{YourMacID}.pdf}, to the Assignment~6
	folder on Avenue under Assessments/Assignments.
	\texttt{\emph{YourMacID}} must be your personal MacID (written without
	capitalization).  The \texttt{Assignment\_6\_\emph{YourMacID}.tex}
	file is a copy of the LaTeX source file for this assignment
	(\texttt{Assignment\_6.tex} found on Avenue under
	Contents/Assignments) with your solution entered after each problem.
	The \texttt{Assignment\_6\_\emph{YourMacID}.pdf} is the PDF output
	produced by executing
	
	\begin{itemize}
		
		\item[] \texttt{pdflatex Assignment\_6\_\emph{YourMacID}}
		
	\end{itemize}
	
	This assignment is due \textbf{Sunday, March 14, 2021 before midnight.}
	You are allow to submit the assignment multiple times, but only the
	last submission will be marked.  \textbf{Late submissions and files
		that are not named exactly as specified above will not be accepted!}
	It is suggested that you submit your preliminary
	\texttt{Assignment\_6\_\emph{YourMacID}.tex} and
	\texttt{Assignment\_6\_\emph{YourMacID}.pdf} files well before the
	deadline so that your mark is not zero if, e.g., your computer fails
	at 11:50 PM on March 14.
	
	\textbf{Although you are allowed to receive help from the
		instructional staff and other students, your submission must be your
		own work.  Copying will be treated as academic dishonesty! If any of
		the ideas used in your submission were obtained from other students
		or sources outside of the lectures and tutorials, you must
		acknowledge where or from whom these ideas were obtained.}
	
	\newpage
	
	\subsection*{Background}
	For any three regular expressions $\alpha$, $\beta$, and $\gamma$, the following properties hold:
	\be
	\item Commutativity of union: $ \alpha + \beta  = \beta + \alpha$
	\item Associativity of union: $ (\alpha + \beta) + \gamma = \alpha + (\beta + \gamma)$
	\item Associativity of concatenation: $(\alpha \beta) \gamma = \alpha (\beta  \gamma)$
	\item Distribution of union: $ \alpha (\beta + \gamma) = \alpha \beta + \alpha  \gamma$ and $  (\beta + \gamma)\alpha =  \beta \alpha +   \gamma \alpha$.
	\item $\emptyset$ is the identity element for union: $\alpha + \emptyset = \alpha$.
	\item $\emptyset$ is the annihilator element for concatenation: $\alpha  \emptyset = \emptyset \alpha = \emptyset$.
	\item $\epsilon$ is the identity element for concatenation: $\alpha  \epsilon = \alpha$.
	\item Idempotence of Kleene star: $\alpha^{**} = \alpha^*$.
	\item Some additional properties of Kleene star:
		\be
			\item $\alpha^* + \epsilon = \alpha^*$
			\item $\alpha^* + \alpha^* = \alpha^*$
			\item $\alpha^*\alpha^* = \alpha^*$
			\item $\alpha\alpha^* + \epsilon = \alpha^*$
			\item $\alpha^*\alpha + \epsilon = \alpha^*$
		\ee
	\ee
	
	\subsection*{Problems}
	
	\be
	
	\item The regular expression $\alpha = (0110 + 01) (10)^*$ can be written in a more simplified way. 
	\be
	\item \textbf{[10 points]} By reasoning based on $L(\alpha)$, define a shorter regular expression equal to $\alpha$. Explain your reasoning.
	\item \textbf{[10 points]} Using the properties explained above, prove that the expression you came up with in (a), is indeed equal to $\alpha$.
	\ee
	
	\bigskip
	
	\textbf{Aamina Hussain, hussaa54, March 14, 2021}

    \medskip    

\ee

\textbf{\emph{part a)}}\\
A shorter regular expression $\beta$ that is equal to $\alpha$ is $\beta = 01(10)^*$. The language that the regular expression $\alpha$ describes says that the string can begin with:
\be
\item 01 followed by an arbitrary amount of 10s, or
\item 0110 followed by an arbitrary number of 10s
\ee
However, in \#2, 0110 ends with 10, meaning it follows strings described in \#1. 0110 is 01 followed by an arbitrary number of 10s, in this case one 10. 0110 is $01(10)^1$. We can therefore remove the 0110 from $\alpha$ in order to shorten it.
\begin{align*}
    &\phantom{{}=} L(\alpha) \\
    &= L((0110+01)(10)^*) & \pnote{sub. for $\alpha$}\\
    &= L(0110+01)L((10)^*) & \pnote{definition of L}\\
    &= (L(0110) \cup L(01))(L(10))^* & \pnote{definition of L}\\
    &= (\{0110\} \cup \{01\})\{10\}^* & \pnote{definition of L}\\
    &= \{0110\}\{10\}^* \cup \{01\}\{10\}^* & \pnote{concat. distributes over union}\\
    &= \{0110\}\{\epsilon, 10, 1010,...\} \cup \{01\}\{\epsilon, 10, 1010,...\} & \pnote{definition of asterate}\\
    &= \{0110, 011010, 01101010,...\} \cup \{01, 0110, 011010,...\} & \pnote{definition of concatenation}\\
\end{align*}
As you can see, the union of the two sets above will result in a set that is equal to the set on the right above. This means that everything in the set on the left is in the set on the right. Therefore, we don't need the set on the left of the union. More specifically, we do not need 0110. Continuing the above calculation below:
\begin{align*}
    &= \{01, 0110, 011010,...\} & \pnote{definition of union}\\
    &= \{01\}\{\epsilon, 10, 1010,...\} & \pnote{definition of concatenation}\\
    &= \{01\}\{10\}^* & \pnote{definiton of asterate}\\
    &= L(01)(L(10))^* & \pnote{definition of L}\\
    &= L(01)L((10)^*) & \pnote{definition of L}\\
    &= L(01(10)^*) & \pnote{definition of L}\\
    &= L(\beta) & \pnote{sub. for $\beta$}\\
\end{align*}


\textbf{\emph{part b)}}
\begin{align*}
    &\phantom{{}=} (0110+01)(10)^* & \pnote{$\alpha$}\\
    &= (0110+01\epsilon)(10)^* & \pnote{$\epsilon$ is the identity element for concatenation}\\
    &= (01(10+\epsilon))(10)^* & \pnote{Distribution of union}\\
    &= 01((10+\epsilon)(10)^*) & \pnote{Associativity of concatenation}\\
    &= 01(10(10)^*+\epsilon(10)^*) & \pnote{Distribution of union}\\
    &= 01(10(10)^*+(10)^*) & \pnote{$\epsilon$ is the identity element for concatenation}\\
    &= 01(10(10)^*+(10)^*+\epsilon) & \pnote{Additional property of Kleene star (9.a)}\\
    &= 01(10(10)^*+\epsilon+(10)^*) & \pnote{Commutativity of union}\\
    &= 01((10)^*+(10)^*) & \pnote{Additional property of Kleene star (9.d)}\\
    &= 01(10)^* & \pnote{Additional property of Kleene star (9.b); $\alpha$ simplified}\\
\end{align*}


\end{document}


